Classless Java: Tuning Java Interfaces

### 2015-11-24 paper/sections/Implementation.tex
implementation revised

\section{Implementation}

One of the downside of Java is the code verbosity, e.g., getter and setter
methods for fields, unneeded type annotation, etc. Lombok project~\cite{} is a
Java tool that aims at removing (or reducing) these boilerplate code as far as
possible, via annotations. There are a number of annotations provided by the
original Lombok, including \textbf{@Getter}, \textbf{@Setter},
\textbf{@ToString} for generating getters, setters and \QM{toString} methods,
respectively.

@@

Our implementation is based on extension to Lombok. In Eclipse, with an
interface annotated by \mixin, the automatic annotation processing is performed
and the information of the interface from compilation is captured in the
``Outline'' window, including all the methods inside the interface as well as
the generated ones.
 The custom transformation is easy and convenient to use.
 For example this means that the IDE functionality 
 content assist autocomplete will work for the newly generated methods.

@@

\paragraph{Limitation}
Our prototype implementation using Lombok has certain limitation: 
\begin{itemize}
\item The prototype does not support separate compilation yet. Currently all
  related interfaces have to appear in a single Java file. Therefore, changes to
  a single interface would require re-compiling the whole file. This compilation
  limitation is not caused by our algorithm. It is Lombok implementation related
  issue: in Lombok it is hard to capture a type declaration from its reference,
  even harder when the type declaration is in other files (we have not found a
  way to do this currently).
\item At this stage our implementation only realizes the Eclipse handler and our
  experiments are all conducted in Eclipse. The implementation for
  \texttt{javac} is missing.
\end{itemize}

>>>>

\section{Implementation with Lombok}

Our implementation is based on extension to Lombok. Lombok project~\cite{lombok}
is a Java tool that aims at removing (or reducing) Java boilerplate code as far
as possible, via annotations. Code verbosity is one of the downside of Java,
usually caused by getter and setter methods for fields, unneeded type
annotation, etc. There are a number of annotations provided by the original
Lombok, including \textbf{@Getter}, \textbf{@Setter}, \textbf{@ToString} for
generating getters, setters and \QM{toString} methods, respectively.

@@

The annotation we created is \mixin. In Eclipse, with an interface annotated by
\mixin, the automatic annotation processing is performed and the information of
the interface from compilation is captured in the ``Outline'' window, including
all the methods inside the interface as well as the generated ones.  The custom
transformation is easy and convenient to use.  For example this means that the
IDE functionality content assist autocomplete will work for the newly generated
methods.

@@

\paragraph{Limitation}
Our prototype implementation using Lombok has certain limitation: 
\begin{itemize}
\item The prototype does not support separate compilation yet. Currently all
  related interfaces have to appear in a single Java file. Therefore, changes to
  a single interface would require re-compiling the whole file. This compilation
  limitation is not caused by our algorithm. It is Lombok implementation related
  issue: in Lombok it is hard to capture a type declaration from its reference,
  even harder when the type declaration is in other files (we have not found a
  way to do this currently).
\item At this stage our implementation only realizes the Eclipse handler and our
  experiments are all conducted in Eclipse. The implementation for
  \texttt{javac} is missing.
\item The current implementation does not take type-parameter polymorphism into
  consideration, thus does not support generics yet.
\end{itemize}
